\Large \bf \projtitle

### 2015-05-07 doc/paper/paper.tex
Fix command spacing

\usepackage{style, verbatim, url, graphicx}
\usepackage[colorlinks=true, citecolor=blue, linkcolor=blue]{hyperref}
\usepackage{caption}
\usepackage{cleveref, breakurl}

@@

\newcommand{\zbf}{Zauberfl\"{o}te}
\newcommand{\projtitle}{\zbf: A Transparent Peer-to-Peer CDN}
\newcommand{\inclfigure}[3]{
    \begin{figure}
        \begin{centering}
            \includegraphics[width=.8\linewidth]{#2}
            \caption{#3}
            \label{#1}
        \end{centering}
    \end{figure}
}

@@

Currently, peer-to-peer content delivery networks do exist, yet are usually
closed-source. PeerCDN~\cite{peercdn} is one such example found in
industry; it offloads site hosting to users of a site, significantly lowering strain on content delivery from a central source. \zbf\ is an open-sourced system
that will allow developers to easily integrate a peer-to-peer CDN to expedite
content delivery to clients even when operating under heavy load.

@@

\section{\zbf\ API}

\zbf\ supports peer-to-peer loading for CSS (via \texttt{link} elements), Javascript (via \texttt{script} elements), and images (via \texttt{img} elements). In order for an existing website to utilize \zbf, the developer simply needs to make two changes to the DOM elements.

The first change that must be made is renaming the \texttt{src} or \texttt{href} attribute to  \texttt{data-zf-fallback}. \zbf\ uses the \texttt{data-zf-fallback} attribute in order to (1) prevent the browser from automatically fetching the resources, and (2) provide a URL to be used in the event that the peer-to-peer network is unable to serve the content.

The second attribute that must be present on a DOM element that is fetched by \zbf\ is the \texttt{data-zf-hash} attribute. The \texttt{data-zf-hash} attribute is the SHA1 hash of that resource, which can be computed by the developer, and is utilized by \zbf\ in order to ensure integrity of data fetched via peer-to-peer interaction.

@@

The \zbf\ architecture consists of several loosely-connected components (see
figure~\ref{fig:components}). At the highest level, there is a download manager that
provides a reliable download service. It relies on the tracker interface and
the connection manager. The tracker interface facilitates communication with
the central tracker for information about peers and file sizes, and the
connection manager provides an interface for peer-to-peer message transfer.

@@

\inclfigure{fig:components}{components.pdf}{
    Relationship between different client-side components of the \zbf\
    peer-to-peer download service. Components in gray are standard browser
    APIs.
}

@@

\zbf\ divides assets into chunks; chunks are individually requested and
sent between peers. We use a standard chunk size of 10240 bytes in our
implementation; preliminary tests showed this chunk size to be reasonable.
When a client asks for a resource, the download manager for that client
determines the number of chunks for that resource from the specified size.
The download manager then evenly distributes requests for these chunks
among the peers with the resource. \\
Requests for chunks time out on a per-chunk basis. We track the time \zbf\
last sent a request for each chunk; if this time exceeds a cutoff, we randomly
choose another peer with the resource and send the chunk request to that
peer. We periodically retrieve an updated peers list for this resource
from the tracker.

@@

When fetching content peer-to-peer, it is necessary to authenticate data that
is downloaded. \zbf\ achieves this by using a cryptographic hash function to
authenticate data that is downloaded. Assets that are to be downloaded
peer-to-peer are identified by their hash, and once the download manager
finishes downloading the content from peers, it verifies that the hash of the
contents matches what is expected. The download manager rejects content if
there is an authentication error. In the current implementation, if this
occurs, the download manager falls back to downloading the content over HTTP
from the fallback URL.

@@

\zbf\ divides assets into chunks primarily to enable parallelization. Because
individual peers may not have high outbound bandwidth, it is beneficial to
download in parallel from many peers. Our implementation parallelizes chunk
downloads, with pending chunk requests balanced between available peers in the
network. If certain peers are slow to respond, the download manager
automatically requests chunks from faster peers to optimize download time.
Parallel downloads help reduce download latency.

@@

There are two main server-side components to \zbf\. First is the tracker,
which maintains a mapping from resource hashes to the peers that have that
resource. Second is the WebRTC handshake channel, which passes information
between peers to enable them to open WebRTC data channels.

@@

\subsection{Per-chunk hash validation}
As of right now, \zbf\ verifies the integrity of the downloaded resource once all chunks have been retrieved and joined. In normal circumstances where all chunks successfully download, this may not prove to be an issue. However, waiting until all chunks are downloaded and combined to verify the file means that if a single chunk had been corrupted or compromised, all chunks for the file would need to be downloaded, combined, and verified again.

An improvement to \zbf\ that would mitigate this issue would be to have the Tracker module provide checksums for each chunk. From the user's perspective, the \texttt{data-zf-hash} attribute currently used to store the hash of the file would be replaced with the hash of the JSON object storing a list of the hashes for each chunk. Upon connection to the tracker, each client would receive that list and verify its integrity, and then be able to verify and redownload each chunk independently in the event of failure..

@@

Another improvement to \zbf\ would be to allow it to parallelize downloads via HTTP and P2P transfers simultaneously. By using the \texttt{Range} HTTP header attribute, \zbf\ could fetch the same data as contained in P2P chunks from the HTTP fallback server. By utilizing both HTTP and P2P, \zbf\ may be able to provide service speed that is expected in all instances to be faster than simply using HTTP alone.

@@

Implementing variation in requested chunk sizes could allow \zbf\ to independently
determine a more optimal chunk size for each asset. For instance, we hypothesize
that different chunk sizes are optimal for differently sized assets, and potentially
for different media types. If \zbf\ more intelligently determined the optimal size
of chunks for each resource, overall download latency would decrease.

@@

If \zbf\ could detect which peers have higher bandwidth connections, and thus
are more capable of swiftly delivering data to a client, \zbf\ could prioritize
requesting data from these peers. Perhaps \zbf\ could request larger chunks from
peers with higher bandwidth connections. \zbf\ could also dynamically react to
poor connections with peers during the chunk requesting process; chunk requests
that subsequently time out could be redistributed more intelligently among
peers with higher bandwidth connections.

\subsection{Support for HTML5 media}
It is possible to add functionality such that \zbf\ can construct \texttt{ReadableStream}s (as specified by the Streams standard) %TODO: cite https://streams.spec.whatwg.org
from the chunks of data as it receives them. Using this stream, the DOM injection layer could feasibly replace HTML5 media elements such as embedded Video and Audio. Since these types of media are particularly large in size, being able to distribute them in a decentralized, peer-to-peer manner could provide substantial load reduction for the central server.

\subsection{Automatic conversion to \zbf }
% TODO

>>>>

\usepackage{style, verbatim, url, graphicx, xspace}
\usepackage[colorlinks=true, citecolor=blue, linkcolor=blue]{hyperref}
\usepackage{caption}
\usepackage{cleveref, breakurl}

@@

\newcommand{\zbf}{Zauberfl\"{o}te\xspace}
\newcommand{\projtitle}{\zbf: A Transparent Peer-to-Peer CDN}
\newcommand{\inclfigure}[3]{
    \begin{figure}
        \begin{centering}
            \includegraphics[width=.8\linewidth]{#2}
            \caption{#3}
            \label{#1}
        \end{centering}
    \end{figure}
}

@@

Currently, peer-to-peer content delivery networks do exist, yet are usually
closed-source. PeerCDN~\cite{peercdn} is one such example found in
industry; it offloads site hosting to users of a site, significantly lowering strain on content delivery from a central source. \zbf is an open-sourced system
that will allow developers to easily integrate a peer-to-peer CDN to expedite
content delivery to clients even when operating under heavy load.

@@

\section{\zbf API}

\zbf supports peer-to-peer loading for CSS (via \texttt{link} elements), Javascript (via \texttt{script} elements), and images (via \texttt{img} elements). In order for an existing website to utilize \zbf, the developer simply needs to make two changes to the DOM elements.

The first change that must be made is renaming the \texttt{src} or \texttt{href} attribute to  \texttt{data-zf-fallback}. \zbf uses the \texttt{data-zf-fallback} attribute in order to (1) prevent the browser from automatically fetching the resources, and (2) provide a URL to be used in the event that the peer-to-peer network is unable to serve the content.

The second attribute that must be present on a DOM element that is fetched by \zbf is the \texttt{data-zf-hash} attribute. The \texttt{data-zf-hash} attribute is the SHA1 hash of that resource, which can be computed by the developer, and is utilized by \zbf in order to ensure integrity of data fetched via peer-to-peer interaction.

@@

The \zbf architecture consists of several loosely-connected components (see
figure~\ref{fig:components}). At the highest level, there is a download manager that
provides a reliable download service. It relies on the tracker interface and
the connection manager. The tracker interface facilitates communication with
the central tracker for information about peers and file sizes, and the
connection manager provides an interface for peer-to-peer message transfer.

@@

\inclfigure{fig:components}{components.pdf}{
    Relationship between different client-side components of the \zbf
    peer-to-peer download service. Components in gray are standard browser
    APIs.
}

@@

\zbf divides assets into chunks; chunks are individually requested and
sent between peers. We use a standard chunk size of 10240 bytes in our
implementation; preliminary tests showed this chunk size to be reasonable.
When a client asks for a resource, the download manager for that client
determines the number of chunks for that resource from the specified size.
The download manager then evenly distributes requests for these chunks
among the peers with the resource. \\
Requests for chunks time out on a per-chunk basis. We track the time \zbf
last sent a request for each chunk; if this time exceeds a cutoff, we randomly
choose another peer with the resource and send the chunk request to that
peer. We periodically retrieve an updated peers list for this resource
from the tracker.

@@

When fetching content peer-to-peer, it is necessary to authenticate data that
is downloaded. \zbf achieves this by using a cryptographic hash function to
authenticate data that is downloaded. Assets that are to be downloaded
peer-to-peer are identified by their hash, and once the download manager
finishes downloading the content from peers, it verifies that the hash of the
contents matches what is expected. The download manager rejects content if
there is an authentication error. In the current implementation, if this
occurs, the download manager falls back to downloading the content over HTTP
from the fallback URL.

@@

\zbf divides assets into chunks primarily to enable parallelization. Because
individual peers may not have high outbound bandwidth, it is beneficial to
download in parallel from many peers. Our implementation parallelizes chunk
downloads, with pending chunk requests balanced between available peers in the
network. If certain peers are slow to respond, the download manager
automatically requests chunks from faster peers to optimize download time.
Parallel downloads help reduce download latency.

@@

There are two main server-side components to \zbf. First is the tracker,
which maintains a mapping from resource hashes to the peers that have that
resource. Second is the WebRTC handshake channel, which passes information
between peers to enable them to open WebRTC data channels.

@@

\subsection{Per-chunk hash validation}
As of right now, \zbf verifies the integrity of the downloaded resource once all chunks have been retrieved and joined. In normal circumstances where all chunks successfully download, this may not prove to be an issue. However, waiting until all chunks are downloaded and combined to verify the file means that if a single chunk had been corrupted or compromised, all chunks for the file would need to be downloaded, combined, and verified again.

An improvement to \zbf that would mitigate this issue would be to have the Tracker module provide checksums for each chunk. From the user's perspective, the \texttt{data-zf-hash} attribute currently used to store the hash of the file would be replaced with the hash of the JSON object storing a list of the hashes for each chunk. Upon connection to the tracker, each client would receive that list and verify its integrity, and then be able to verify and redownload each chunk independently in the event of failure..

@@

Another improvement to \zbf would be to allow it to parallelize downloads via HTTP and P2P transfers simultaneously. By using the \texttt{Range} HTTP header attribute, \zbf could fetch the same data as contained in P2P chunks from the HTTP fallback server. By utilizing both HTTP and P2P, \zbf may be able to provide service speed that is expected in all instances to be faster than simply using HTTP alone.

@@

Implementing variation in requested chunk sizes could allow \zbf to independently
determine a more optimal chunk size for each asset. For instance, we hypothesize
that different chunk sizes are optimal for differently sized assets, and potentially
for different media types. If \zbf more intelligently determined the optimal size
of chunks for each resource, overall download latency would decrease.

@@

If \zbf could detect which peers have higher bandwidth connections, and thus
are more capable of swiftly delivering data to a client, \zbf could prioritize
requesting data from these peers. Perhaps \zbf could request larger chunks from
peers with higher bandwidth connections. \zbf could also dynamically react to
poor connections with peers during the chunk requesting process; chunk requests
that subsequently time out could be redistributed more intelligently among
peers with higher bandwidth connections.

\subsection{Support for HTML5 media}
It is possible to add functionality such that \zbf can construct \texttt{ReadableStream}s (as specified by the Streams standard) %TODO: cite https://streams.spec.whatwg.org
from the chunks of data as it receives them. Using this stream, the DOM injection layer could feasibly replace HTML5 media elements such as embedded Video and Audio. Since these types of media are particularly large in size, being able to distribute them in a decentralized, peer-to-peer manner could provide substantial load reduction for the central server.

\subsection{Automatic conversion to \zbf}
% TODO
